Robust Clustering for Ad Hoc Cognitive Radio Network

### 2017-12-10 journal-draft/ettdoc_JG.tex
revison based on james' comments on 5th Dec

\section{Centralized Solution for Robust Clustering}
\label{centralized_solution}
%XXXXXX
%Di: The first paragraph has been revised based on the first batch of comments for the camera-ready version, but somehow get lost in the last version. I take some parts from your revision and keep some from my revision.
We now turn to algorithms that can solve the CRN robust clustering problem, despite its complexity. 
We initially consider a centralized solution for this problem.
Assuming some global knowledge of the CRN to be given at some point in the network, \ie the locations of primary users and their working channels, and the locations of secondary users and available channels on them, we can propose a centralized scheme.
We obtain the set of $\mathcal{S}$ which contains all the clusters which satisfy the definition of cluster in Section~\ref{sec:model}.
$\mathcal{S}$ is basically a powerset of $\mathcal{N}$, which nevertheless is restricted by connectivity and spectrum availability in the network.
There are $\mathcal{S}=\{C_1, C_2, \ldots, C_{|\mathcal{S}|}\}$ \footnote{The subscript $i$ means the $i$-th cluster in $\mathcal{S}$.} and $|\mathcal{S}| = M$.
Then the problem as defined in Definition~\ref{def_centralized_clustering} can be formulated as a binary linear programming problem and can be solved by many available solvers:
\begin{equation}
\begin{aligned}
     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p(C_i)) \\
     &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, \text{for}\,\,\forall j=1, \ldots, N \\
   &&& \Sigma_{j=1}^N x_{ij} = |C_i|\cdot y_i,\, \text{for}\,\,\forall i=1, \ldots, M \\
  % &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
   &&& i\in \{1,2, \cdots M\}, \hspace{0.3cm} j\in \{1,2,\cdots N\}
%\notag
\end{aligned}
\label{centralized_opt}
\end{equation}
$y_i$ and $x_{ij}$ are the two sets of binary optimization variables.
Being either 1 or 0, $y_i$ denotes whether the $i$-th cluster $C_i$ in $\mathcal{S}$ is chosen or not.
$x_{ij}$ indicates whether the CR node $j$ resides in the cluster $C_i$, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$.

@@

%The optimization is a binary linear programming problem.
As to the objective function, the sum of the first items is the sum of CCs of the clusters which constitute the CRN.
In the second item, we propose $p(C_i)$ which is a size-related weight for cluster $C_i, i\in{1,\cdots, M}$.
$p(C_i)$ is positively related with the difference between $C_i$'s size and the desired size $\delta$.
When $y_i$ is 1 ($C_i$ is chosen) but $|C_i|$ doesn't equal to the desired cluster size $\delta$, the second item is negative, which contradicts the direction of the optimization.
Thus the second item discourages the appearance the clusters whose sizes deviate from the desired cluster size $\delta$.
The weight $p(C_i)$ with respect to different cluster sizes is as follows,
%$$
%p(C_i) = \left\{ \begin{array}{rl}
%0 &\mbox{ if $|C_i|=\delta$} \\
%\rho_1 &\mbox{if $||C_i|-1|=\delta$} \\
%\rho_2 &\mbox{if $||C_i|-2|=\delta$} \\
%\vdots\\
%\rho_\sigma &\mbox{if $||C_i|-\sigma|=\delta$} \\
%\end{array} \right.
%$$

>>>>

\section{Centralized Solution for Robust Clustering}
\label{centralized_solution}
%XXXXXX%
%Di: The first paragraph has been revised based on the first batch of comments for the camera-ready version, but somehow get lost in the last version. I take some parts from your revision and keep some from my revision.
We now turn to algorithms that can solve the CRN robust clustering problem, despite its complexity. 
We initially consider a centralized solution for this problem.
Assuming some global knowledge of the CRN to be given at some point in the network, \ie the locations of primary users and their working channels, and the locations of secondary users and available channels on them, we can propose a centralized scheme.
We obtain the set of $\mathcal{S}$ which contains all the clusters which satisfy the definition of cluster in Section~\ref{sec:model}.
$\mathcal{S}$ is basically a powerset of $\mathcal{N}$, which nevertheless is restricted by connectivity and spectrum availability in the network.
There are $\mathcal{S}=\{C_1, C_2, \ldots, C_{|\mathcal{S}|}\}$ \footnote{The subscript $i$ means the $i$-th cluster in $\mathcal{S}$.} and $|\mathcal{S}| = M$.
Then the problem as defined in Definition~\ref{def_centralized_clustering} can be formulated as a binary linear programming problem and can be solved by many available solvers:
\begin{equation}
\begin{aligned}
     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p(C_i)) \\
     &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, \text{for}\,\,\forall j=1, \ldots, N \\
   &&& \Sigma_{j=1}^N x_{ij} = |C_i|\cdot y_i,\, \text{for}\,\,\forall i=1, \ldots, M \\
  % &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
   &&& i\in \{1,2, \cdots M\}, \hspace{0.3cm} j\in \{1,2,\cdots N\}
%\notag
\end{aligned}
\label{centralized_opt}
\end{equation}
$y_i$ and $x_{ij}$ are the two sets of binary optimization variables.
Being either 1 or 0, $y_i$ denotes whether the $i$-th cluster $C_i$ in $\mathcal{S}$ is chosen or not.
$x_{ij}$ indicates whether the CR node $j$ resides in the cluster $C_i$, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$.
$q_{ij}$ is a constant and it equals $|K(C_i)|$ when node $j\in C_i$.
$q_{ij}$ equals zero when node $j\notin C_i$.

@@

%The optimization is a binary linear programming problem.
As to the objective function, the sum of the first term in the bracket over all clusters in $\mathcal{S}$ and all CR node in $\mathcal{N}$ is the sum of CCs of the clusters which constitute the CRN.
In the second term in the bracket, we propose $p(C_i)$ which is a size-related weight for cluster $C_i, i\in{1,\cdots, M}$.
$p(C_i)$ is positively related with the difference between $C_i$'s size and the desired size $\delta$.
When $y_i$ is 1 ($C_i$ is chosen) but $|C_i|$ doesn't equal to the desired cluster size $\delta$, the second item is negative, which contradicts the direction of the optimization.
Thus the second item discourages the appearance the clusters whose sizes deviate from the desired cluster size $\delta$.
The weight $p(C_i)$ with respect to different cluster sizes is as follows,
%$$
%p(C_i) = \left\{ \begin{array}{rl}
%0 &\mbox{ if $|C_i|=\delta$} \\
%\rho_1 &\mbox{if $||C_i|-1|=\delta$} \\
%\rho_2 &\mbox{if $||C_i|-2|=\delta$} \\
%\vdots\\
%\rho_\sigma &\mbox{if $||C_i|-\sigma|=\delta$} \\
%\end{array} \right.
%$$
